### 2016-05-04 outline.tex
add chad's answers to outline

\vskip.3in
\section{Main Idea}
Adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on eqm path
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute?)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
					\item Does Congressional uncertainty transfer over to ITC uncertainty? NEED to argue that it does if we're going to use the political uncertainty data that I'm generating
				\end{itemize}
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years); 4 for safeguard
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Political uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}

@@

\vskip.5in
\section{Cross-industry Variation}
\begin{itemize}
	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
		\begin{itemize}
			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
			\item \textbf{Q}: Is it really exogenous? What does data say about whether renewals are at same level as original TTB?
		\end{itemize}
	\item Industry / lobby gets richer / more insulated for five years (or poorer if not insulated enough)
		\begin{itemize}
			\item This could lead to differences in budget constraint if that were in model
			\item May not need budget constraint if extra budget allows them to invest in technology or politics
				\begin{itemize}
					\item Come to question of whether protection and technological upgrading are complements or substitutes
					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
						\begin{itemize}
							\item Is there an incentive to \textit{not} get stronger technologically?
						\end{itemize}
					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
				\end{itemize}
			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
				\begin{itemize}
					\item \textbf{Q}: This is one of the arguments for escape clause, no?
				\end{itemize}
		\end{itemize}
	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
		\begin{itemize}
			\item If the dist'n doesn't change, only the outcome, I'd just be observing draws from the same distribution, driven by same behavior.
			\item I guess this is something I want to be able to tease apart? \textit{If} uncertainty plays an important role, is it just the outcome that's changing, or the underlying uncertainty and thus the behavior?
			\item Can I get at this with the data I have (i.e. \textit{will} have, shortly)?
		\end{itemize}
\end{itemize}

>>>>

\vskip.3in
\section{Main Idea}
Adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on eqm path
			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
				\begin{itemize}
					\item Directly about strength of evidence? (indirectly about retaliation / dispute?)
					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors? 
					\textbf{A}: (Per Chad's email on 4/26/16, his and Gene Grossman's 2008 WTR) The data is useless b/c Commerce has never used counterfactual analysis.
					\item Does Congressional uncertainty transfer over to ITC uncertainty? NEED to argue that it does if we're going to use the political uncertainty data that I'm generating
				\end{itemize}
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years); 4 for safeguard
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years? \textbf{A}: broadly looks true in data (to my casual glance)
			\item Safeguards are rarely renewed (retaliation allowed after 3 years)
		\end{itemize}
	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
		\begin{itemize}
			\item Political uncertainty could be an answer, \textit{and} it varies across industry
			\item \textbf{Q}: Is this a plausible story?
		\end{itemize}
	\item Also have to adapt model to cross-industry to get necessary variation
		\begin{itemize}
			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
		\end{itemize}
\end{itemize}

@@

\vskip.5in
\section{Cross-industry Variation}
\begin{itemize}
	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
		\begin{itemize}
			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
			\item \textbf{Q}: Is it really exogenous? What does data say about whether renewals are at same level as original TTB?
			\item \textbf{A}: The statements are of the form ``As a result of the respective determinations by the Department and the ITC that revocation of the antidumping duty order on CTL plate from the PRC and termination of the Agreements on CTL plate from Russia and Ukraine would likely lead to continuation or recurrence of dumping and material injury to an industry in the United States, pursuant to section 751(d)(2) of the Act, the Department hereby gives notice of the continuation of the antidumping duty order on CTL plate from the PRC and the continuation of the Agreements on CTL plate from Russia and Ukraine. The effective dates of continuation will be the date of publication in the Federal Register of this Continuation Notice. Pursuant to sections 751(c)(2) and 751(c)(6) of the Act, the Department intends to initiate the next five-year sunset reviews of the antidumping duty order on CTL plate from the PRC and the Agreements on CTL plate from Russia and Ukraine not later than November 2019.'' \url{https://www.federalregister.gov/articles/2015/12/21/2015-32022/continuation-of-antidumping-duty-order-on-certain-cut-to-length-carbon-steel-plate-from-the-peoples}
		\end{itemize}
	\item Industry / lobby gets richer / more insulated for five years (or poorer if not insulated enough)
		\begin{itemize}
			\item This could lead to differences in budget constraint if that were in model
			\item May not need budget constraint if extra budget allows them to invest in technology or politics
				\begin{itemize}
					\item Come to question of whether protection and technological upgrading are complements or substitutes
					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
						\begin{itemize}
							\item Is there an incentive to \textit{not} get stronger technologically?
						\end{itemize}
					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
				\end{itemize}
			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
				\begin{itemize}
					\item \textbf{Q}: This is one of the arguments for escape clause, no?
				\end{itemize}
		\end{itemize}
	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC/DOC's decision-making process
		\begin{itemize}
			\item DOC initiates sunset review, determines whether dumping would continue
			\item ITC investigates whether expiry of AD would lead to recurrence or continuation of injury
		\end{itemize}
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
		\begin{itemize}
			\item If the dist'n doesn't change, only the outcome, I'd just be observing draws from the same distribution, driven by same behavior.
			\item I guess this is something I want to be able to tease apart? \textit{If} uncertainty plays an important role, is it just the outcome that's changing, or the underlying uncertainty and thus the behavior?
			\item Can I get at this with the data I have (i.e. \textit{will} have, shortly)?
		\end{itemize}
\end{itemize}
